\begin{declarationcontribution}
    \addchaptertocentry{\contributionname} % Add the declaration to the table of contents
    \noindent I, \authorname (\textbf{SY}), declare that this Master's thesis titled, \enquote{Similarity and As- sociation: Principles of Distributed Semantic Processing in the Human Brain} and the work presented in it could not been accomplished without the help from the advisors of my research internship: Sabine \textsc{Ploux} (\textbf{SP}), Laurent \textsc{Bonnasse-Gahot} (\textbf{LBG}) and Christophe \textsc{Pallier} (\textbf{CP}).
    
    \begin{itemize} 
    \item \textbf{SP} helped enormously with the initial research problem definition and hypothesis formulation. Together with \textbf{LBG} and \textbf{CP}, they've given a rich literature collection on the relevant domain including brain encoding/decoding, theories on paradigmatic/syntagmatic axes.
    \item \textbf{CP} and Snezana \textsc{Todorovic} designed the MRI experiment, prepared audio stimuli, textual reference data and behavioral control procedures. \textbf{CP} preprocessed MRI data including data cleaning and normalization. These acquisitions were performed as part of the project ``Neural Computational Models of Natural Language'', financed by the NSF--ANR (PI: John Hale and Christophe Pallier).
    \item \textbf{SY} implemented automatic pipelines and carried out a large part of rule-based and manual correction of transcribed fMRI stimuli lemmatisation and semantic space vocabulary alignment. \textbf{SP} helped the verification of the results.
    \item \textbf{SY} adopted multiple semantic model validation tasks and dataset, implemented the initial iteration of dataset translation and correction, which is later perfected by \textbf{SP}.
    \item \textbf{SY} adapted publicly available algorithms and tested combinations of hyper-parameter configurations to build one of the semantic representation models.
    \item \textbf{LBG} actively participated in the conception of semantic space dissociation algorithm, which is later implemented and tested by \textbf{SY}. 
    \item \textbf{SP} visually examined iterations of the resulting semantic embedding models and assured the their quality and coherence.
    \item \textbf{CP} shared the fMRI analysis code base developed by him and collaborators. This project heavily depended on the regressor generation, design matrix orthogonalization functions of the library. \textbf{CP} also shared the computed feature of acoustic energy. \textbf{SY} added upon the code base functions to perform nested GridSearch regressions, implemented multiple statistical tests and result visualization pipelines.
    \item \textbf{LBG} and \textbf{CP} actively participated in the analysis and interpretation of fMRI regression results. They also gave useful guidance on the utilization of \code{nilearn, nibabel, nistat} libraries and analytical procedures including statistical tests and ROI analysis.
    \item \textbf{SY} drafted the Master's thesis, which is attentively proofread by \textbf{SP} and \textbf{LBG} multiple times. \textbf{SP} also gave thoughtful insights on psycholinguistic discussion of the obtained results. \textbf{LBG} offered countless redactional good-practice advice during the drafting, which helped shaping this thesis.
    \end{itemize}
     
\end{declarationcontribution}

\clearpage